---
title: "Statistical Inference Assignment, Part B"
author: "Teja Kodali"
date: "22 March 2015"
output: word_document
---

## Overview
Here, we will investigate the ToothGrowth data in the R datasets package. We
will load the ToothGrowth data, perform some basic data analysis and provide a
summary of the data. We will use confidence intervals and hypotheses tests to
compare tooth growth by supp and dose.

## Loading the data
```{r}
library(ggplot2)
library(datasets)
data(ToothGrowth)
str(ToothGrowth)
head(ToothGrowth)
```

## Plotting
```{r}
plot <- ggplot(ToothGrowth, 
               aes(x=factor(dose),y=len,fill=factor(dose)))
plot + geom_boxplot(notch=F) + facet_grid(.~supp) +
     scale_x_discrete("Dosage (Milligram)") +   
     scale_y_continuous("Length of Teeth") +  
     ggtitle("Variation of teeth length with dosage")

```

As we can see, the length of the teeth is higher when dosage is higher,
regardless of whether it was Orange Juice of Vitamin C.

## Summary of data
```{r}
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
summary(ToothGrowth)
```
```{r}
table(ToothGrowth$supp, ToothGrowth$dose)

```


## Confidence intervals and hypotheses tests
```{r}
supp.t1 <- t.test(len~supp, paired=F, var.equal=T, data=ToothGrowth)
supp.t2 <- t.test(len~supp, paired=F, var.equal=F, data=ToothGrowth)
supp.result <- data.frame("p-value"=c(supp.t1$p.value, supp.t2$p.value),
                          "Conf-Low"=c(supp.t1$conf[1],supp.t2$conf[1]),
                          "Conf-High"=c(supp.t1$conf[2],supp.t2$conf[2]),
                          row.names=c("Equal Var","Unequal Var"))
supp.result
```

## Conclusions
Based on the analysis above, we can conclude that 

1. The 2mg dose has larger impact on tooth growth than 1mg and 0.5mg, while 1mg 
dose has more impact than 0.5mg dose. So there is a different in the growth of 
the tooth while the doses are larger.

2. There is no doubt that Orange Juice and Vitamin C have obvious different 
impact on tooth growth.

## Assumptions
It is assumed that

1. There are no other supplements consumed by the subjects.

2. Orange Juice and Vitamin C are the only two factors influencing the growth of
the teeth.
